Paradigms in Physics 2.0

### 2017-06-27 paper.tex
count cards

\section{Paradigms 2.0 process}
We began the Paradigms 2.0 process in the Winter of 2016, having in
the previous year obtained faculty agreement, and support from our
Department head.  The process was spearheaded by a committee of four
(the authors DR, LG, EM, and CAM, with EvZ present at meetings
documenting our process).  During the Winter quarter, we informed the
community of our process through a colloquium, and collected student
and faculty perspectives on the existing curriculum.  We then
interviewed faculty who recently taught each of our existing courses
to document topics that were currently covered.  This resulted in a
total of XXX index cards in YYY stacks, corresponding to courses, with
cards color coded by broad topic.

>>>>

\section{Paradigms 2.0 process}
We began the Paradigms 2.0 process in the Winter of 2016, having in
the previous year obtained faculty agreement, and support from our
Department head.  The process was spearheaded by a committee of four
(the authors DR, LG, EM, and CAM, with EvZ present at meetings
documenting our process).  During the Winter quarter, we informed the
community of our process through a colloquium, and collected student
and faculty perspectives on the existing curriculum.  We then
interviewed faculty who recently taught each of our existing courses
to document topics that were currently covered.  This resulted in a
total of $\sim$700 index cards in $\sim$30 stacks, with each stack
corresponding to one course, and each card describing a topic,
color-coded as in Fig.~\ref{fig:schedule}.
